---
title: "Data aquisition"
subtitle: "Exercise 4: Poll data story"
author: "Markus Kollberg & Ivo Bantel"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# relevant packages
library(tidyverse)
library(KFAS)

party_cols <- c(
    cducsu = "#000000",
    afd    = "#0489DB",
    spd    = "#E3000F",
    grune  = "#1AA037",
    linke  = "#E3000F",
    fdp    = "#FFEF00",
    bsw    = "#A7402E"
)
```

## Introduction

In this exercise, we are trying to identify the largest swing in the data for all parties.

## 4.1: Get trends

First, we need to get the trends from the data for the previous exercise. For this, we'll use the `KFAS` package and the `KFAS::KFS()` function.

```{r get_trend, include=TRUE}


```

## 4.2: Get largest "swing"

Second, let's define and compute the swings per party by comparing values according to our definition, and inspect the overall swings.

```{r find_swing, include=TRUE}



```

And finally, let's find the _single largest swing_ for each party in our data.

```{r find_largest_swing, include=TRUE}

```
