---
title: "Data aquisition"
subtitle: "Exercise 2: Web scraping & Poll aggregation"
author: "Markus Kollberg & Ivo Bantel"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# relevant packages
library(tidyverse)
library(rvest)
library(purrr)
library(dplyr)
library(janitor)
```

## Introduction

Next, we'll embark on a slightly bigger project. Let's imagine we're interested in German political winds and want to use polling data to visualize this.

But as good data journalists, we're not just interested in _a poll_. We're interested in all polls and more so, we're interested in *all polls over time*, similar to POLITICO's *Poll of Polls* (e.g. [Germany](https://www.politico.eu/europe-poll-of-polls/germany) or [Czechia](https://www.politico.eu/europe-poll-of-polls/czech-republic)).

For this, we'll proceed step by step. First, we're using another aspect of data acquisition: *web scraping* using the `rvest` package.

## Exercise 2.1: Data acquisition through web scraping

To obtain the data, we need a page providing German polling data. Luckily for us, [wahlrecht.de](https://www.wahlrecht.de) provides these data readily available.

The goal of this task is to obtain a data set from the sub pages of `https://www.wahlrecht.de/umfragen`

**Task 2.1**:

- retrieve tables from the relevant pages (`https://www.wahlrecht.de/umfragen/allensbach.htm`, `https://www.wahlrecht.de/umfragen/emnid.htm`, `https://www.wahlrecht.de/umfragen/forsa.htm`, `https://www.wahlrecht.de/umfragen/politbarometer.htm`, `https://www.wahlrecht.de/umfragen/gms.htm`, `https://www.wahlrecht.de/umfragen/dimap.htm`, `https://www.wahlrecht.de/umfragen/insa.htm`, `https://www.wahlrecht.de/umfragen/yougov.htm`)

- clean the result

- concatenate into one table


```{r scraping_wahlrecht, warning=FALSE}

# 1. data scraping ----
urls_list <- c("https://www.wahlrecht.de/umfragen/allensbach.htm",
               "https://www.wahlrecht.de/umfragen/emnid.htm")

final_dataset <- data.frame()

for (url in urls_list){
  
  current_page <- read_html(url)
  current_table <- current_page %>% 
    html_nodes(.,css=".wilko") 
  
  current_formatted_table <- current_table %>%
    html_table() %>% 
    as.data.frame() %>% 
    mutate(Source=url)
  
  final_dataset <- bind_rows(final_dataset,current_formatted_table)
}

# 2. Clean data ----

clean_data <- final_dataset %>% 
  select(Date=1,`CDU.CSU`:Sonstige) %>% 
  slice(-(1:5)) %>% 
  mutate(across(everything(), ~ if_else(.x =="–", NA, .x))) %>% 
  mutate(across(everything(), ~ str_replace_all(.x, "%", ""))) %>% 
  mutate(across(everything(), ~ str_replace_all(.x, ",", "."))) %>% 
  mutate(across(`CDU.CSU`:Sonstige, ~ as.numeric(.))) %>% 
  mutate(Date=as.Date(Date,format = "%d.%m.%Y"))

```

The result of this step should be a data set (e.g. `tibble`) containing something similar to this:
```{r example_result_scraping_wahlrecht, echo=F}
structure(list(institute = c("Allensbach", "Allensbach", "Allensbach", 
"Allensbach", "Allensbach", "Allensbach"), date = c("19.04.2025", 
"27.03.2025", "21.02.2025", "13.02.2025", "23.01.2025", "20.12.2024"
), cducsu = c(27, 29.5, 32, 32, 34, 36), spd = c(16, 16, 14.5, 
15, 17, 16), grune = c(12, 11.5, 12, 13, 13.5, 12), fdp = c(3, 
3, 4.5, 5, 4, 4), linke = c(10, 10, 7.5, 6, NA, NA), afd = c(23.5, 
21, 20, 20, 20, 18), bsw = c(4, 4, 4.5, 4, 5, 6), befragte = c(1.048, 
1.031, 1.064, 1.021, 1.015, 1.006)), row.names = c(NA, -6L), class = c("tbl_df", 
"tbl", "data.frame"))
```


## Exercise 2.2: Visualizing scraped complicate data

Next, we want to present these data and visualize polling aggregation trends over time.

If you didn't succeed with the scraping or (more likely) the cleaning entirely: let us know so we can help.

Afterwards, you can use [this](https://www.dropbox.com/scl/fi/ub04b3zho4drtrw3pbqre/DE_wahlrecht_polls_student-copy.csv?rlkey=rsk0fhbuly3v8aewe0foxhytm&dl=0) data set

We want to plot individual polls as dots and trends over time as lines. The color codes have been loaded for you already.

```{r visualization_colors}
party_cols <- c(
    cducsu = "#000000",
    afd    = "#0489DB",
    spd    = "#E3000F",
    grune  = "#1AA037",
    linke  = "#E3000F",
    fdp    = "#FFEF00",
    bsw    = "#A7402E"
)
```

This data is already fairly clean (as we have pre-cleaned with the scraping). So it only requires minimal adjustments for plotting. 

Use `ggplot2` to create a smoothed line chart overlaying a scatter plot.

```{r visualizing_german_polls, warning=FALSE, message=FALSE}

wide_format <- clean_data %>% 
  pivot_longer(cols=`CDU.CSU`:Sonstige,
               names_to="Political Party",
               values_to="Vote Percentage")
  

visualisation <- ggplot(wide_format,aes(x=Date,y=`Vote Percentage`,color=`Political Party`))+
  geom_point(size=1, color="black",alpha=0.1)+
  geom_smooth(stat="smooth", se=FALSE)+
  #scale_colour_manual(values=party_cols)+
  theme_minimal()+
  labs(title="German Voter Preferences",
       x="Year",
       y="Vote Intention(%)")

```

### Exercise 2.3 (Bonus!): Adding to plot

If you want to go beyond this:

- add polling error intervals based on sample sizes
- add election "ground truth" into plot and adjust the trends

```{r visualizing_german_polls_bonus, warning=FALSE, message=FALSE}

# your code here

```
