---
title: "Data aquisition"
subtitle: "Exercise 3: Advanced data acquisition"
author: "Markus Kollberg & Ivo Bantel"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load required libraries
library(rvest)
library(tidyverse)
```



## Assisted data research

Next, we're tackling another aspect of data acquisition: in-depth research of more complex data sources.

**Task**
- Find out how to get the data underlying the _*European Network of Transmission System Operators*_ (https://www.entsoe.eu/data/map).

Feel free to use LLMs etc.

The **"solution"** should not entail written code but an understanding of how you can retrieve the needed data through the API


## API

**Task**
- Get the actual total load (in MAW) for Germany over the last 30 days using the ENTSO-E API
- Visualize the data with the `entsoeapi` package
- you will need an access token for this. Ask us if you get here.

``` {r entsoe_api, include=TRUE}

library(entsoeapi) #remotes::install_github("krose/entsoeapi")
library(lubridate)
library(purrr)

# Set token
Sys.setenv(ENTSOE_PAT="")


```

*hint* use the function `entsoeapi::load_actual_total()`

